\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

\title{Amazon cell phones evaluation platform}


\author{Kristina Satara \\
  {\tt  kristina.satara@epfl.ch} \\\And
  Alexandre Rassinoux \\
  {\tt  alexandre.rassinoux@epfl.ch} \\\And
Marion Kramer \\
{\tt  marion.kramer@epfl.ch} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
  Buying products from Amazon can be risky. Reviews help when making decision which product to buy, as they give users more product details and personal experience. Since everybody who wants to buy a product from Amazon usually spends some time reading the reviews and ratings, we decided to create evaluation platform which would help the users decide by giving them insight into model's downsides and advantages based on the reviews.

This platform will use reviews and extract meaningful information from it, and then evaluate certain product based on these reviews. We will use sentiment analysis to classify each of the reviews (and it's parts) as good or bad. Based on this we will describe each model. Some of the specifications that will be taken into account are the ergonomy, battery, memory, etc. If we have enough time, we will try to see how the reviews changed during the time for each model, or in other words to see if some models improved during the time.
\end{abstract}

\section{Introduction}

\section{Related Work}

\section{Data Collection}
Should be brief

\section{Dataset Description with Summary Statistics}

\section{Methods}
Methods with math and description of main algorithm

\section{Results and Findings}

\section{Conclusion}




\end{document}

